\section{\sc Publications in Preparation}
\begin{enumerate}
\item[{1.}] {\bf Stein,~L.~C.}, Yagi,~K. (2013)
  {\it Scalar corrections beyond general relativity}.
\end{enumerate}

% \section{\sc Submitted Publications}
% \begin{enumerate}
% \item[{1.}] Yagi,~K., {\bf Stein,~L.~C.}, Yunes,~N., Tanaka,~T. (2013)
%   {\it Isolated and Binary Neutron Stars in Dynamical Chern-Simons
%     Gravity}, \href{http://arxiv.org/abs/1302.1918}{arXiv:1302.1918}
% \end{enumerate}

\section{\sc Refereed Publications}
\begin{enumerate}
\item[{8.}] Yagi,~K., {\bf Stein,~L.~C.}, Yunes,~N., Tanaka,~T. (2013)
  {\it Isolated and Binary Neutron Stars in Dynamical Chern-Simons
    Gravity},
  \href{http://arxiv.org/abs/1302.1918}{Phys. Rev. D {\bf 87} 084058}
\item[{7.}] Yagi,~K., {\bf Stein,~L.~C.}, Yunes,~N.,
  Tanaka,~T. (2012), {\it Post-Newtonian, Quasi-Circular Binary
    Inspirals in Quadratic Modified Gravity},
  \href{http://arxiv.org/abs/1110.5950}{Phys. Rev. D {\bf 85} 064022}
\item[{6.}] Vigeland,~S., Yunes,~N., {\bf Stein,~L.~C.} (2011), {\it
    Bumpy black holes in alternative theories of gravity},
  \href{http://arxiv.org/abs/1102.3706}{Phys. Rev. D {\bf 83} 104027}
\item[{5.}] Yunes,~N., {\bf Stein,~L.~C.} (2011), {\it Nonspinning
    black holes in alternative theories of gravity},
  \href{http://arxiv.org/abs/1101.2921}{Phys. Rev. D {\bf 83} 104002}
\item[{4.}] {\bf Stein,~L. C.}, Yunes,~N. (2011), {\it Effective
    gravitational wave stress-energy tensor in alternative theories of
    gravity},
  \href{http://arxiv.org/abs/1012.3144}{Phys. Rev. D {\bf 83} 064038}
\item[{3.}] Lutomirski,~A., Tegmark,~M., Sanchez,~N.~J., {\bf
    Stein,~L.~C.},
  Urry,~W.~L., Zaldarriaga,~M. (2011), {\it Solving the
    corner-turning problem for large interferometers},
  \href{http://arxiv.org/abs/0910.1351}{MNRAS {\bf 410} 2075}
\item[{2.}] Sutton,~P., Jones,~G., Chatterji,~S., Kalmus,~P., Leonor,~I.,
  Poprocki,~S., Rollins,~J., Searle,~A., {\bf Stein,~L.}, Tinto,~M.,
  Was,~M. (2010), {\it X-Pipeline: an analysis package for autonomous
    gravitational-wave burst searches},
  \href{http://arxiv.org/abs/0908.3665}{New J. Phys. {\bf 12} 053034}
\item[{1.}] Chatterji,~S., Lazzarini,~A., {\bf Stein,~L.}, Sutton,~P.,
  Searle,~A. (2006), {\it Coherent network analysis technique for
    discriminating gravitational-wave bursts from instrumental noise},
  \href{http://arxiv.org/abs/gr-qc/0605002}{Phys. Rev. D {\bf 74}, 082005}
\end{enumerate}

\section{\sc Unrefereed Publications}
\begin{enumerate}
\item[{4.}] {\bf Stein,~L.~C.} (2012), {\it Probes of Strong-field Gravity}, Ph.D. thesis at Massachusetts Institute of Technology
\item[{3.}] Betancourt,~M., {\bf Stein,~L.~C.} (2011) {\it The
    Geometry of Hamiltonian Monte Carlo}, \href{http://arxiv.org/abs/1112.4118}{arXiv:1112.4118}
\item[{2.}] {\bf Stein,~L.~C.} (2009), {\it Binary Inspiral
    Gravitational Waves from a Post-Newtonian Expansion}, Contribution
  to the Wolfram Demonstrations Project, \url{http://demonstrations.wolfram.com/BinaryInspiralGravitationalWavesFromAPostNewtonianExpansion/}
\item[{1.}] {\bf Stein,~L.~C.} (2006), {\it Gravitational Wave Burst Source Localization in a Coherent Network Analysis}, Senior thesis at California Institute of Technology
\end{enumerate}
